%\documentclass[PhD]{iitddiss}
%\documentclass[MS]{iitddiss}
% \documentclass[MTech]{iitddiss}
\documentclass[Dual]{iitddiss}
%\documentclass[BTech]{iitddiss}
% \documentclass[Other]{iitddiss}
% IF YOU USE THE OTHER OPTION, THEN YOU MUST FILL OUT THE PROGRAM OPTION BELOW TOO
% \program{My Fancy Degree}

% \usepackage{times}
 \usepackage{t1enc}

\usepackage{graphicx}
\usepackage{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage{subcaption}
\usepackage{float}
\setcounter{secnumdepth}{3}
\linespread{1.2}

\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

\fancyhf{}

\rhead{\fancyplain{}{\thepage}} % predefined ()
\lhead{\fancyplain{}{\rightmark}} % 1. sectionname, 1.1 subsection name etc
\cfoot{\textcopyright \text{ } \the\year, \emph{Indian Institute of Technology Delhi}}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page

\title{ESTIMATION OF URBANISATION IN INDIAN DISTRICTS}

\author{Aditi Singla}
\authortwo{Prachi Singh}
\advisor{Prof. Aaditeshwar Seth}
\entrynumber{2014CS50277}
\entrynumbertwo{2014CS50289}
\date{June 2019}
\department{Computer Science and Engineering}

%\nocite{*}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
\certificate

\vspace*{0.5in}

\noindent This is to certify that the thesis titled {\bf ESTIMATION OF 
URBANISATION IN INDIAN DISTRICTS}, submitted by {\bf Aditi Singla} and 
{\bf Prachi Singh}, to the Indian Institute of Technology, Delhi, for
the award of the degree of {\bf Bachelor and Master of Technology}, is 
a bonafide record of the research work done by them under our supervision. 
The contents of this thesis, in full or in parts, have not been submitted
to any other Institute or University for the award of any degree or
diploma.

\vspace*{3in}

\begin{singlespacing}
\noindent {\bf Prof. Aaditeshwar Seth} \\
\noindent Professor \\
\noindent Dept. of Computer Science \& Engineering\\
\noindent IIT-Delhi, 600 036 \\
\end{singlespacing}
\vspace*{0.25in}
\\
\noindent Place: New Delhi \\
\noindent Date: 27th June 2019


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
\acknowledgements

We would like to wholeheartedly thank our advisor Prof. Aaditeshwar Seth 
for guiding us at each and every step of our project work. He helped us 
in learning on how to approach a problem by looking from different 
perspectives and taking a step back to see the bigger picture, which we 
would carry for the rest of our careers.   

We would also like to thank Bipul, Ayush, Dibyajyoti, Arpit and Shyam with 
whom we had long and valuable discussions on various issues that we faced 
and the possible approaches we could take. We are also grateful to the Google 
Earth community for answering our numerous queries on their discussion forums
and helping us in every way possible. We would also like to extend our thanks 
to the staff of CSE and SIT departments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract

\abstract

\noindent KEYWORDS: \hspace*{0.5em} \parbox[t]{4.4in}{Urbanisation; LANDSAT8;
  Settlement Delineation; Spatial Analysis; Extent of Urbanisation; Patterns of
  Urbanisation; India.}

\vspace*{24pt}

\noindent Recently, there has been a rapid increase in the population, 
especially in the developing nations like India. The existing cities have 
expanded and new settlement areas have been established. Although this has 
lifted the people in rural regions out of poverty, many factors like health, 
resource availability, etc. have been compromised. We here attempt to 
understand urbanisation and give a mechanism to estimate it, which can then 
help the government in better health planning and resource allocation.

This problem has got a lot of attention in the community and various attempts 
have been made to use census data, satellite imagery data and social media data 
collection, to obtain the above mentioned attributes and give an urbanisation 
estimate. We use the technique of spatial analysis using remotely sensed satellite 
data to give and urbanisation estimate. We define urbanisation as the extent and 
the distribution of change in built-up regions. To achieve this, we perform 
settlement delineation by applying pixel-wise classification models on the satellite 
imagery to generate an estimate of built-up regions at district level. Once this is 
done, we perform a temporal analysis on the spatial distribution of the built-up 
regions to generate these parameters to represent the urbanisation index.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}

% \listoftables
% \addcontentsline{toc}{chapter}{LIST OF TABLES}
% \listoffigures
% \addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
% \abbreviations

% \noindent
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{IITD}   \> Indian Institute of Technology, Delhi \\
% \textbf{RTFM} \> Read the Fine Manual \\
% \end{tabbing}

% \pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

% \chapter*{\centerline{NOTATION}}
% \addcontentsline{toc}{chapter}{NOTATION}

% \begin{singlespace}
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{$r$}  \> Radius, $m$ \\
% \textbf{$\alpha$}  \> Angle of thesis in degrees \\
% \textbf{$\beta$}   \> Flight path in degrees \\
% \end{tabbing}
% \end{singlespace}

\pagebreak
\clearpage

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction.

\chapter{INTRODUCTION}
\label{chap:intro}

\input{introduction}

\chapter{BACKGROUND}
\label{chap:background}

\input{background}

\chapter{PROPOSED METHODOLOGY: OVERVIEW}
\label{chap:outline}

\input{outline}

\chapter{PROPOSED METHODOLOGY: COMPONENT-WISE}
\label{chap:methodology}

\input{methodology}

\chapter{RESULTS}
\label{chap:results}

\input{results}

\chapter{CONCLUSION}
\label{chap:conclusion}

\input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices.

% \appendix

% \chapter{A SAMPLE APPENDIX}

% Just put in text as you would into any chapter with sections and
% whatnot.  Thats the end of it.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.

\begin{singlespace}
  \bibliography{refs}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List of papers

% \listofpapers

% \begin{enumerate}
% \item Authors....  \newblock
%  Title...
%   \newblock {\em Journal}, Volume,
%   Page, (year).
% \end{enumerate}

\end{document}